AAAI Press Formatting Instructions \\for Authors Using \LaTeX{} --- A Guide

### 2021-09-17 publications/iaai21/dora_outlier_detection_iaai.tex
Add results and figure for fmnist experiment
Add text for fmnist dataset and results sections

\subsection{Datasets}
We constructed three datasets to evaluate the utility of DORA and the
performance of each ranking algorithm for a variety of scientific domains
 (astrophysics, planetary science, and Earth science). We also included a 
 benchmark dataset that uses MNIST and FashionMNIST. Here we describe
 the details of each dataset.
\todo{Maybe add
 a table with number of samples, number of reference known outliers (if 
 available), etc, if room? }
 \todo{Can we make any of these datasets publicly available with the paper?}

@@

\subsubsection{MNIST and FashionMNIST.}
We added this to demonstrate the capabilities of DORA with a traditional
benchmark dataset. \todo{Bryce.}

@@

    \hline
    Astrophysics &   &   &   \\
    Earth & 6,757  &  37 & 76  \\
    Planetary &   &   &   \\
    (F)MNIST &   &   &   \\
    \hline
  \end{tabular}
\end{table}

@@

\todo{Bryce: add results for (F)MNIST use case.}

\begin{table}
  \caption{Precision at $N=n_{outlier}$ for three applications; the
  best result for each data set is in bold.}
  \label{tab:faw_results}
  \centering
  \begin{tabular}{l|cccc}
    \hline
    Algorithm & Astro. & Earth & Planetary & FMNIST \\
    \hline
    PCA               & & 0.41 & 0.44 \\
    DEMUD             & & 0.41 & 0.44 \\
    \hline
    RX                & & 0.43 & ---- \\
    LRX               & & ---- & 0.33 \\
    \hline
    Iso. Forest  & & 0.46 & \textbf{0.56} \\
    \hline
    PAE               & & 0.41 & 0.44 \\
    Neg. Sampling & & \textbf{0.49} & 0.33 \\
    \hline
    Random            & & 0.32 & 0.11 \\
    \hline
  \end{tabular}
\end{table}

@@

>>>>

\subsection{Datasets}
We constructed three datasets to evaluate the utility of DORA and the
performance of each ranking algorithm for a variety of scientific domains
 (astrophysics, planetary science, and Earth science). We also included a 
 benchmark dataset that uses MNIST and Fashion-MNIST. Here we describe
 the details of each dataset.
\todo{Maybe add
 a table with number of samples, number of reference known outliers (if 
 available), etc, if room? }
 \todo{Can we make any of these datasets publicly available with the paper?}

@@

\subsubsection{MNIST and Fashion-MNIST.}
We included MNIST and F-MNIST to demonstrate the capabilities of DORA with a
traditional benchmark dataset. In this experiment, we used 60,000 images from 
F-MNIST as the training set and a combined set of 2,000 images from MNIST and 
F-MNIST as the evaluation set. Well-discriminating algorithms should assign 
higher outlier scores to samples from MNIST than F-MNIST.

@@

    \hline
    Astrophysics &   &   &   \\
    Earth & 6,757 & 37 & 76  \\
    Planetary &   &   &   \\
    F-MNIST & 60,000 & 1,000 & 1,000  \\
    \hline
  \end{tabular}
\end{table}

@@

For the MNIST and F-MNIST dataset, PCA and DEMUD tied for the highest precision,
while DEMUD, PCA, and PAE tied for the highest MDR. Negative sampling had the 
lowest performance in both metrics.

\begin{table}
  \caption{Precision at $N=n_{outlier}$ for three applications; the
  best result for each data set is in bold.}
  \label{tab:faw_results}
  \centering
  \begin{tabular}{l|cccc}
    \hline
    Algorithm & Astro. & Earth & Planetary & F-MNIST \\
    \hline
    PCA               & & 0.41 & 0.44 & \textbf{0.84} \\
    DEMUD             & & 0.41 & 0.44 & \textbf{0.84} \\
    \hline
    RX                & & 0.43 & ---- & 0.82 \\
    LRX               & & ---- & 0.33 & 0.56 \\
    \hline
    Iso. Forest  & & 0.46 & \textbf{0.56} & 0.74 \\
    \hline
    PAE               & & 0.41 & 0.44 & 0.83 \\
    Neg. Sampling & & \textbf{0.49} & 0.33 & 0.43 \\
    \hline
    Random            & & 0.32 & 0.11 & 0.49 \\
    \hline
  \end{tabular}
\end{table}

@@

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{figures/fmnist_combined_plot.pdf}
    \caption{Number of true outliers ranked in top $N$ selections for 
    F-MNIST dataset.}
    \label{fig:fmnist_results}
\end{figure}
